Super-resolution of Aeromagnetic Survey Data

### 2023-10-12 discussion.tex
Consolidate bibliography at end of doc

\printbibliography{}

@@

To the best of my knowledge, \Cref{ch:paper1} presents the first investigation in the literature of the super-resolution enhancement of gridded aerogeophysical data.
Prior to this work, it was unknown how well SR methods developed for natural images would adapt to the features and high dynamic range present within magnetic grids, or the challenges faced in developing a training dataset for these data.
We established that the CNN SR methods RDN\textdaggerdbl{} and ESRGAN+ could be trained to upsample low-resolution textures in magnetic grids by a factor of four, and that the results were more accurate than bicubic upsampling in the real-world case study region.
The ESRGAN+ method used in \Cref{ch:paper2} enhanced resolution, however it introduced significant spurious features, masking the enhancement.
Hence, the method based on RDN\textdaggerdbl{} was preferred.
We identified the need for additional representative training data to investigate transferability of the method to other geological domains, and a realistic method to generate low-resolution training data.

@@

The contribution in \Cref{ch:paper3} used coordinate multilayer perceptron neural networks to learn a representation of the function that describes a surveyed potential field extent.
To my knowledge, this is the first time implicit neural representation of aerogeophysical survey data has been reported in the literature.
It was seen that these networks are highly suited for processing spatial data such as point sampled geophysics surveys.
The contribution is capable of predicting regularly spaced grids from scattered survey point data, and can be used as a novel method to calculate derivatives of a potential field from the learnt representation, both task which are fundamental to interpretation and processing in geophysics.
By commencing the methods from point sample data, the number of individual processing steps is reduced, and the application is fully trainable.
Continued advances in the recent field of CMLPs will improve the capacity of the method for representing high-resolution aeromagnetic data.

>>>>

% \printbibliography{}

@@

To the best of the author's knowledge, \Cref{ch:paper1} presents the first investigation in the literature of the super-resolution enhancement of gridded aerogeophysical data.
Prior to this work, it was unknown how well SR methods developed for natural images would adapt to the features and high dynamic range present within magnetic grids, or the challenges faced in developing a training dataset for these data.
We established that the CNN SR methods RDN\textdaggerdbl{} and ESRGAN+ could be trained to upsample low-resolution textures in magnetic grids by a factor of four, and that the results were more accurate than bicubic upsampling in the real-world case study region.
The ESRGAN+ method used in \Cref{ch:paper2} enhanced resolution, however it introduced significant spurious features, masking the enhancement.
Hence, the method based on RDN\textdaggerdbl{} was preferred.
We identified the need for additional representative training data to investigate transferability of the method to other geological domains, and a realistic method to generate low-resolution training data.

@@

The contribution in \Cref{ch:paper3} used coordinate multilayer perceptron neural networks to learn a representation of the function that describes a surveyed potential field extent.
To the author's knowledge, this is the first time implicit neural representation of aerogeophysical survey data has been reported in the literature.
It was seen that these networks are highly suited for processing spatial data such as point sampled geophysics surveys.
The contribution is capable of predicting regularly spaced grids from scattered survey point data, and can be used as a novel method to calculate derivatives of a potential field from the learnt representation, both task which are fundamental to interpretation and processing in geophysics.
By commencing the methods from point sample data, the number of individual processing steps is reduced, and the application is fully trainable.
Continued advances in the recent field of CMLPs will improve the capacity of the method for representing high-resolution aeromagnetic data.
